### 2015-07-30 Harris_2015/manuscript-materials/draft.Rmd
appeasing the editor

For the Markov networks, I used the rosalia package [@harris_rosalia_2015],
as described above. Given the large number of parameters associated with
some of the networks to  be estimated, I regularized the likelihood
using a logistic prior distribution with a scale of 2 on the $\alpha$ and
$\beta$ terms.  This convex prior distribution has a similar shape to the
Laplace distribution used in LASSO regularization (especially in the tails),
but does not force the estimates to be exactly zero.

I also evaluated five alternative methods from the existing literature to
calibrate the performance of the Markov network as a method for estimating
species interactions. The first two alternative interaction measures were the
sample correlations and the partial correlations between each pair of species'
data vectors on the landscape [@albrecht_spatial_2001; @faisal_inferring_2010].
Because partial correlations are undefined for landscapes with
perfectly-correlated species pairs, I used a regularized estimate based on
James-Stein shrinkage, as implemented in the corpcor package’s `pcor.shrink`
function with the default settings [@REF]. In the context of non-Gaussian
data, the partial correlation can be thought of as a computationally efficient
approximation to the full Markov network model [@loh_structure_2013].

@@

Because the different methods mostly describe species interactions on different
scales (e.g. correlations versus $Z$ scores versus regression coefficients), I used
linear regression through the origin to rescale the different estimates produced
by each method so that they had a consistent interpretation. After rescaling each
method’s estimates, I calculated squared errors between the scaled interaction
estimates and “true” interaction values for each of the [[N]] species pairs
across all the simulated data sets. These squared errors determined the
proportion of variance explained for different combinations of method and
landscape size (compared with a baseline model that assumed all interaction
strengths to be zero).

>>>>

<!-- exp(qlogis(.975, scale = 2)) -->

For the Markov networks, I used the rosalia package [@harris_rosalia_2015],
as described above. For the analyses with 20 species, I added a very weak
logistic prior distribution on the $\alpha$ and $\beta$ terms with scale 2 to
ensure that the model estimates were always finite. The bias introduced by this
prior should be small: the 95% credible interval on $\beta$ indicates that one
species' presence should not generally affect the odds of observing a different
species by more than a factor of 1500 (which is not much of a constraint). The
logistic distribution was chosen because it is convex and has a similar shape to
the Laplace distribution used in LASSO regularization (especially in the tails),
but it is differentiable everywhere and does not force any estimates to be
exactly zero.

I also evaluated five alternative methods from the existing literature to
calibrate the performance of the Markov network as a method for estimating
species interactions. The first two alternative interaction measures were the
sample correlations and the partial correlations between each pair of species'
data vectors on the landscape [@albrecht_spatial_2001; @faisal_inferring_2010].
Because partial correlations are undefined for landscapes with
perfectly-correlated species pairs, I used a regularized estimate based on
James-Stein shrinkage, as implemented in the corpcor package’s `pcor.shrink`
function with the default settings [@REF]. In the context of non-Gaussian
data, the partial correlation can be thought of as a computationally efficient
approximation to the full Markov network model [@loh_structure_2013]. This sort
of model is very common for drawing inferences about interaction networks in
bioinformatics contexts [@REF].

@@

For the larger landscapes, I evaluated the relationship between each method's
estimates and the "true" interaction strengths among all of the species that
were observed to occur across the simulated landscapes. This kind of evaluation
is important because ecologists need a consistent way to know how strong species
interactions are regardless of which species were present in a particular data
set or how many observations were taken. Because the different methods mostly
describe species interactions on different scales (e.g. correlations versus $Z$
scores versus regression coefficients), I used linear regression through the
origin to rescale the different estimates produced by each method so that they
had a consistent interpretation. After rescaling each method’s estimates, I
calculated squared errors between the scaled interaction estimates and “true”
interaction values for each of the [[N]] species pairs across all the simulated
data sets. These squared errors determined the proportion of variance explained
for different combinations of method and landscape size (compared with a
baseline model that assumed all interaction strengths to be zero).
